Weighted Model Counting with Conditional Probabilities

### 2020-07-14 paper.tex
Fix an encoding bug caused by overly eager optimisation

\item In preliminary results, the SBK05 encoding gives the wrong asnwer in 60
  QMR instances (all with evidence files). Sometimes that answer is $\gg 1$.
\item Similarly, cd06 is supposed to be the fastest, but seems to be one of the
  slowest (along with cd05). Perhaps the best encoding for arithmetic circuits
  has very little to do with the best encoding for CNF WMC solvers?

@@

>>>>

\item cd06 is supposed to be the fastest, but seems to be one of the slowest
  (along with cd05). Perhaps the best encoding for arithmetic circuits has very
  little to do with the best encoding for CNF WMC solvers?

@@

\item Zero-probability weights and one-probability weights can be interpreted as
  logical clauses. This doesn't affect ADDMC but could be useful for other
  solvers.
\item Filtering out ADDs that have nothing to do with the answer helps
  tremendously, but I'm not sure if I should do that.
\item For each row in each CPT, we order values by decreasing probabilities.
  Need to check if this makes the solver more accurate.
